Ionization of biological molecules by multicharged ions by using the stoichiometric model

### 2019-09-21 NewMonti25.tex
new figures included in tex

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
\caption{Scaled total ionization cross section of six atomic targets 
by impact of multicharged projectiles.}
\label{fig:atomscaling}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
\caption{Mean emitted energy distribution for ionization by impact of
multicharged ions. Charge state of projectiles given by arrow.}
\label{fig:emittedener}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
\caption{Mean emitted angle distribution for ionization by impact of
multicharged ions.}
\label{fig:emittedang}
\end{figure}

@@

We report the total ionization cross sections by the impact of 
multicharged ions for adenine, cytosine, guanine and thymine in 
Fig.~\ref{fig:crossDNA_1}. For adenine, the agreement with the 
experimental data available~\cite{iriki2011} is very good 
in our range of validity. To the best of our knowledge, there are not 
experimental data on ion--collision ionization for the rest of the 
molecules. We included electron impact measurements~\cite{rahman2016} 
with the corresponding equivelocity 
conversion for incident energies higher than 500~keV. In this region, 
the proton and electron cross section should agree. Although the electron 
impact measurements are above our findings for all the molecular targets, 
it is worth stating that our results agree very well with other 
theoretical predictions~\cite{mozejko2003,tan2018}. 
%The symbols used to make reference to the proton and electron experimental data will be kept for subsequent figures.

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
\caption{Scaled ionization cross section by impact of multicharged ions. 
Experiments: 
$\circ$~\cite{iriki2011} for proton impact and $\square$~\cite{rahman2016} 
for electron impact with equivelocity conversion.}
\label{fig:crossDNA_1}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
\caption{Scaled ionization cross section by impact of multicharged ions. 
Experiments: proton impact on $\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
THF~\cite{wang2016}. Impact of $\ominus$ C$^{+4}$, 
$\boxminus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and
$\triangle\mkern-14mu-$ O$^{+8}$, F$^{+8}$ on 
uracil~\cite{agnihotri2012,agnihotri2013}. 
Symbols~$\rhd$~\cite{bug2017}, $\lhd$~\cite{wolf2019}, and 
$\medstar$~\cite{fuss2009} for electron impact with equivelocity conversion.}
\label{fig:crossDNA_2}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
\caption{Scaled ionization cross section per weakly bound electron using
(a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
$\nu_{\alpha}^{\text{CDW}}$. Experiments: proton impact on 
$\circ$ adenine~\cite{iriki2011}, $\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$ 
THF~\cite{wang2016}; electron impact on $\rhd$ pyrimidine~\cite{bug2017},
and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
\label{fig:newscaling}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
\includegraphics[width=\textwidth]{figuras/atomicscaling.eps}
\caption{Scaled total ionization cross section of six atomic targets 
by impact of multicharged projectiles.}
\label{fig:atomscaling}
\end{figure}

@@

\begin{figure}[t!]
\centering
%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
\includegraphics[width=\textwidth]{figuras/ener_mean.eps}
\caption{Mean emitted energy distribution for ionization by impact of
multicharged ions. Charge state of projectiles given by arrow.}
\label{fig:emittedener}
\end{figure}

@@

\begin{figure}[t!]
\centering
%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
\includegraphics[width=\textwidth]{figuras/ang_mean.eps}
\caption{Mean emitted angle distribution for ionization by impact of
multicharged ions.}
\label{fig:emittedang}
\end{figure}

@@

We report the total ionization cross sections by the impact of 
multicharged ions for adenine, cytosine, guanine and thymine in 
Fig.~\ref{fig:crossDNA_1}. For adenine, the agreement with the 
experimental data available~\cite{iriki2011} is very good 
in our range of validity. To the best of our knowledge, there are not 
experimental data on ion--collision ionization for the rest of the 
molecules. We included electron impact measurements~\cite{rahman2016} 
with the corresponding equivelocity 
conversion for incident energies higher than 500~keV. In this region, 
the proton and electron cross section should agree. Although the electron 
impact measurements are above our findings for all the molecular targets, 
it is worth stating that our results agree very well with other 
theoretical predictions~\cite{mozejko2003,tan2018}.

\begin{figure}[t!]
\centering
%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
\includegraphics[width=\textwidth]{figuras/adn1.eps}
\caption{Scaled ionization cross section by impact of multicharged ions. 
Experiments: 
$\circ$~\cite{iriki2011} for proton impact and $\square$~\cite{rahman2016} 
for electron impact with equivelocity conversion.}
\label{fig:crossDNA_1}
\end{figure}

@@

\begin{figure}[t!]
\centering
%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
\includegraphics[width=\textwidth]{figuras/adn2.eps}
\caption{Scaled ionization cross section by impact of multicharged ions. 
Experiments: proton impact on $\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
THF~\cite{wang2016}. Impact of $\ominus$ C$^{+4}$, 
$\boxminus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and
$\triangle\mkern-14mu-$ O$^{+8}$, F$^{+8}$ on 
uracil~\cite{agnihotri2012,agnihotri2013}. 
Symbols~$\rhd$~\cite{bug2017}, $\lhd$~\cite{wolf2019}, and 
$\medstar$~\cite{fuss2009} for electron impact with equivelocity conversion.}
\label{fig:crossDNA_2}
\end{figure}

@@

\begin{figure}[t!]
\centering
%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
\includegraphics[width=\textwidth]{figuras/molscaling85.eps}
\caption{Scaled ionization cross section per weakly bound electron using
(a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
$\nu_{\alpha}^{\text{CDW}}$. Experiments: proton impact on 
$\circ$ adenine~\cite{iriki2011}, $\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$ 
THF~\cite{wang2016}; electron impact on $\rhd$ pyrimidine~\cite{bug2017},
and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
\label{fig:newscaling}
\end{figure}
